### 2015-01-13 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012: Added sections in abstract for figures
DelCo 2012 Report: Figures in appendix.

>>>>

\section{Test 1 Figures}
\label{subsec:Test_1_Figures}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Eastside_Array}
	\caption{Test 1 (FSE1): Eastside Array}
	\label{fig:Test_1_Eastside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Westside_Array}
	\caption{Test 1 (FSE1): Westside Array}
	\label{fig:Test_1_Westside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Hallway_Array}
	\caption{Test 1 (FSE1): Hallway Array}
	\label{fig:Test_1_Hallway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Doorway_Array}
	\caption{Test 1 (FSE1): Doorway Array}
	\label{fig:Test_1_Doorway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Eastside_Array}
	\caption{Test 1 (FSE1): Suppression Eastside Array}
	\label{fig:Test_1_Suppression_Eastside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Westside_Array}
	\caption{Test 1 (FSE1): Suppression Westside Array}
	\label{fig:Test_1_Suppression_Westside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Hallway_Array}
	\caption{Test 1 (FSE1): Suppression Hallway Array}
	\label{fig:Test_1_Suppression_Hallway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Doorway_Array}
	\caption{Test 1 (FSE1): Suppression Doorway Array}
	\label{fig:Test_1_Suppression_Doorway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Eastside}
	\caption{Test 1 (FSE1): Eastside Heat Flux}
	\label{fig:Test_1_Eastside_Heat_Flux}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Westside}
	\caption{Test 1 (FSE1): Westside Heat Flux}
	\label{fig:Test_1_Westside_Heat_Flux}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Hallway}
	\caption{Test 1 (FSE1): Hallway Heat Flux}
	\label{fig:Test_1_Hallway_Heat_Flux}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Near_Fire_Room}
	\caption{Test 1 (FSE1): Heat Flux Near Fire Room}
	\label{fig:Test_1_Heat_Flux_Near_Fire_Room}
\end{figure}

\subsection{Velocity}
\label{subsec:Velocity}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_1_Hallway_Velocity}
	\caption{Test 1 (FSE1): Hallway Velocity}
	\label{fig:Test_1_Hallway_Velocity}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_1_Doorway_Velocity}
	\caption{Test 1 (FSE1): Doorway Velocity}
	\label{fig:Test_1_Doorway_Velocity}
\end{figure}

\section{Test 2 Figures}
\label{subsec:Test_2_Figures}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Eastside_Array}
	\caption{Test 2 (FSW2): Eastside Array}
	\label{fig:Test_2_Eastside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Westside_Array}
	\caption{Test 2 (FSW2: Westside Array}
	\label{fig:Test_2_Westside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Hallway_Array}
	\caption{Test 2 (FSW2): Hallway Array}
	\label{fig:Test_2_Hallway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Doorway_Array}
	\caption{Test 2 (FSW2): Doorway Array}
	\label{fig:Test_2_Doorway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Eastside_Array}
	\caption{Test 2 (FSW2): Suppression Eastside Array}
	\label{fig:Test_2_Suppression_Eastside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Westside_Array}
	\caption{Test 2 (FSW2): Suppression Westside Array}
	\label{fig:Test_2_Suppression_Westside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Hallway_Array}
	\caption{Test 2 (FSW2): Suppression Hallway Array}
	\label{fig:Test_2_Suppression_Hallway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Doorway_Array}
	\caption{Test 2 (FSW2): Suppression Doorway Array}
	\label{fig:Test_2_Suppression_Doorway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Eastside}
	\caption{Test 2 (FSW2): Eastside Heat Flux}
	\label{fig:Test_2_Eastside_Heat_Flux}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Westside}
	\caption{Test 2 (FSW2): Westside Heat Flux}
	\label{fig:Test_2_Westside_Heat_Flux}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Hallway}
	\caption{Test 2 (FSW2): Hallway Heat Flux}
	\label{fig:Test_2_Hallway_Heat_Flux}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Near_Fire_Room}
	\caption{Test 2 (FSW2): Heat Flux Near Fire Room}
	\label{fig:Test_2_Heat_Flux_Near_Fire_Room}
\end{figure}

\subsection{Velocity}
\label{subsec:Velocity}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_2_Hallway_Velocity}
	\caption{Test 2 (FSW2): Hallway Velocity}
	\label{fig:Test_2_Hallway_Velocity}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_2_Doorway_Velocity}
	\caption{Test 2 (FSW2): Doorway Velocity}
	\label{fig:Test_2_Doorway_Velocity}
\end{figure}

\section{Test 3 Figures}
\label{subsec:Test_3_Figures}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Eastside_Array}
	\caption{Test 3 (FSW3): Eastside Array}
	\label{fig:Test_3_Eastside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Westside_Array}
	\caption{Test 3 (FSW3: Westside Array}
	\label{fig:Test_3_Westside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Hallway_Array}
	\caption{Test 3 (FSW3): Hallway Array}
	\label{fig:Test_3_Hallway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Doorway_Array}
	\caption{Test 3 (FSW3): Doorway Array}
	\label{fig:Test_3_Doorway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Eastside_Array}
	\caption{Test 3 (FSW3): Suppression Eastside Array}
	\label{fig:Test_3_Suppression_Eastside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Westside_Array}
	\caption{Test 3 (FSW3): Suppression Westside Array}
	\label{fig:Test_3_Suppression_Westside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Hallway_Array}
	\caption{Test 3 (FSW3): Suppression Hallway Array}
	\label{fig:Test_3_Suppression_Hallway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Doorway_Array}
	\caption{Test 3 (FSW3): Suppression Doorway Array}
	\label{fig:Test_3_Suppression_Doorway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Eastside}
	\caption{Test 3 (FSW3): Eastside Heat Flux}
	\label{fig:Test_3_Eastside_Heat_Flux}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Westside}
	\caption{Test 3 (FSW3): Westside Heat Flux}
	\label{fig:Test_3_Westside_Heat_Flux}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Hallway}
	\caption{Test 3 (FSW3): Hallway Heat Flux}
	\label{fig:Test_3_Hallway_Heat_Flux}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Near_Fire_Room}
	\caption{Test 3 (FSW3): Heat Flux Near Fire Room}
	\label{fig:Test_3_Heat_Flux_Near_Fire_Room}
\end{figure}

\subsection{Velocity}
\label{subsec:Velocity}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_3_Hallway_Velocity}
	\caption{Test 3 (FSW3): Hallway Velocity}
	\label{fig:Test_3_Hallway_Velocity}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_3_Doorway_Velocity}
	\caption{Test 3 (FSW3): Doorway Velocity}
	\label{fig:Test_3_Doorway_Velocity}
\end{figure}

\section{Test 4 Figures}
\label{subsec:Test_4_Figures}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Eastside_Array}
	\caption{Test 4 (FSE4): Eastside Array}
	\label{fig:Test_4_Eastside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Westside_Array}
	\caption{Test 4 (FSE4): Westside Array}
	\label{fig:Test_4_Westside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Hallway_Array}
	\caption{Test 4 (FSE4): Hallway Array}
	\label{fig:Test_4_Hallway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Doorway_Array}
	\caption{Test 4 (FSE4): Doorway Array}
	\label{fig:Test_4_Doorway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Eastside_Array}
	\caption{Test 4 (FSE4): Suppression Eastside Array}
	\label{fig:Test_4_Suppression_Eastside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Westside_Array}
	\caption{Test 4 (FSE4): Suppression Westside Array}
	\label{fig:Test_4_Suppression_Westside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Hallway_Array}
	\caption{Test 4 (FSE4): Suppression Hallway Array}
	\label{fig:Test_4_Suppression_Hallway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Doorway_Array}
	\caption{Test 4 (FSE4): Suppression Doorway Array}
	\label{fig:Test_4_Suppression_Doorway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Eastside}
	\caption{Test 4 (FSE4): Eastside Heat Flux}
	\label{fig:Test_4_Eastside_Heat_Flux}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Westside}
	\caption{Test 4 (FSE4): Westside Heat Flux}
	\label{fig:Test_4_Westside_Heat_Flux}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Hallway}
	\caption{Test 4 (FSE4): Hallway Heat Flux}
	\label{fig:Test_4_Hallway_Heat_Flux}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Near_Fire_Room}
	\caption{Test 4 (FSE4): Heat Flux Near Fire Room}
	\label{fig:Test_4_Heat_Flux_Near_Fire_Room}
\end{figure}

\subsection{Velocity}
\label{subsec:Velocity}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_4_Hallway_Velocity}
	\caption{Test 4 (FSE4): Hallway Velocity}
	\label{fig:Test_4_Hallway_Velocity}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_4_Doorway_Velocity}
	\caption{Test 4 (FSE4): Doorway Velocity}
	\label{fig:Test_4_Doorway_Velocity}
\end{figure}

\section{Test 5 Figures}
\label{subsec:Test_5_Figures}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Eastside_Array}
	\caption{Test 5 (FSE5): Eastside Array}
	\label{fig:Test_5_Eastside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Westside_Array}
	\caption{Test 5 (FSE5): Westside Array}
	\label{fig:Test_5_Westside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Hallway_Array}
	\caption{Test 5 (FSE5): Hallway Array}
	\label{fig:Test_5_Hallway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Doorway_Array}
	\caption{Test 5 (FSE5): Doorway Array}
	\label{fig:Test_5_Doorway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Eastside_Array}
	\caption{Test 5 (FSE5): Suppression Eastside Array}
	\label{fig:Test_5_Suppression_Eastside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Westside_Array}
	\caption{Test 5 (FSE5): Suppression Westside Array}
	\label{fig:Test_5_Suppression_Westside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Hallway_Array}
	\caption{Test 5 (FSE5): Suppression Hallway Array}
	\label{fig:Test_5_Suppression_Hallway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Doorway_Array}
	\caption{Test 5 (FSE5): Suppression Doorway Array}
	\label{fig:Test_5_Suppression_Doorway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Eastside}
	\caption{Test 5 (FSE5): Eastside Heat Flux}
	\label{fig:Test_5_Eastside_Heat_Flux}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Westside}
	\caption{Test 5 (FSE5): Westside Heat Flux}
	\label{fig:Test_5_Westside_Heat_Flux}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Hallway}
	\caption{Test 5 (FSE5): Hallway Heat Flux}
	\label{fig:Test_5_Hallway_Heat_Flux}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Near_Fire_Room}
	\caption{Test 5 (FSE5): Heat Flux Near Fire Room}
	\label{fig:Test_5_Heat_Flux_Near_Fire_Room}
\end{figure}

\subsection{Velocity}
\label{subsec:Velocity}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_5_Hallway_Velocity}
	\caption{Test 5 (FSE5): Hallway Velocity}
	\label{fig:Test_5_Hallway_Velocity}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_5_Doorway_Velocity}
	\caption{Test 5 (FSE5): Doorway Velocity}
	\label{fig:Test_5_Doorway_Velocity}
\end{figure}

\section{Test 6 Figures}
\label{subsec:Test_6_Figures}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Eastside_Array}
	\caption{Test 6 (FSW6): Eastside Array}
	\label{fig:Test_6_Eastside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Westside_Array}
	\caption{Test 6 (FSW6: Westside Array}
	\label{fig:Test_6_Westside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Hallway_Array}
	\caption{Test 6 (FSW6): Hallway Array}
	\label{fig:Test_6_Hallway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Doorway_Array}
	\caption{Test 6 (FSW6): Doorway Array}
	\label{fig:Test_6_Doorway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Eastside_Array}
	\caption{Test 6 (FSW6): Suppression Eastside Array}
	\label{fig:Test_6_Suppression_Eastside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Westside_Array}
	\caption{Test 6 (FSW6): Suppression Westside Array}
	\label{fig:Test_6_Suppression_Westside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Hallway_Array}
	\caption{Test 6 (FSW6): Suppression Hallway Array}
	\label{fig:Test_6_Suppression_Hallway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Doorway_Array}
	\caption{Test 6 (FSW6): Suppression Doorway Array}
	\label{fig:Test_6_Suppression_Doorway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Eastside}
	\caption{Test 6 (FSW6): Eastside Heat Flux}
	\label{fig:Test_6_Eastside_Heat_Flux}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Westside}
	\caption{Test 6 (FSW6): Westside Heat Flux}
	\label{fig:Test_6_Westside_Heat_Flux}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Hallway}
	\caption{Test 6 (FSW6): Hallway Heat Flux}
	\label{fig:Test_6_Hallway_Heat_Flux}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Near_Fire_Room}
	\caption{Test 6 (FSW6): Heat Flux Near Fire Room}
	\label{fig:Test_6_Heat_Flux_Near_Fire_Room}
\end{figure}

\subsection{Velocity}
\label{subsec:Velocity}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_6_Hallway_Velocity}
	\caption{Test 6 (FSW6): Hallway Velocity}
	\label{fig:Test_6_Hallway_Velocity}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_6_Doorway_Velocity}
	\caption{Test 6 (FSW6): Doorway Velocity}
	\label{fig:Test_6_Doorway_Velocity}
\end{figure}

\section{Test 7 Figures}
\label{subsec:Test_7_Figures}

\subsection{Velocity}
\label{subsec:Velocity}

\section{Test 8 Figures}
\label{subsec:Test_8_Figures}

\subsection{Velocity}
\label{subsec:Velocity}
